working title Compatibility system and stigma size are the main predictors of heterospecific pollen effect

### 2019-03-04 Manuscript_draft/Manuscript_draft.Rmd
edits

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.width=6,fig.height=5, fig.cap="A"}
library(ape)
library(phytools)
pollen_tree=read.tree("Data/pollen_tree.nwk")
plot(pollen_tree)
add.scale.bar(x=0, y=1, length = 0.01)
```

>>>>

\newpage
```{r, echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, fig.width=6,fig.height=5, fig.cap="A"}
library(ape)
library(phytools)
library(png)

pollen_tree=read.tree("Data/pollen_tree.nwk")

plot(pollen_tree)
add.scale.bar(x=0, y=1, length = 0.01)

a <- readPNG("images/tomato.png")
b <- readPNG("images/bra_colour.png")
c <- readPNG("images/ipomoea.png")

rasterImage(image=a, xleft=0.08,ybottom=1,
            xright=1.2,ytop=3.6)
rasterImage(image=b, xleft=0.15,ybottom=7,xright=0.18,ytop=10)

rasterImage(image=c, xleft=0.15,ybottom=4,xright=0.18,ytop=7)
